---
title: "Group Project Team 4"
author: "Alejandro Avila, Anthony Ramirez, Benjamin B An, Chengze Liu, Vishu Kodikanti"
format: pdf
editor: visual
---

## 

```{r}
#importing the data set and displaying the summary
strength<-read.csv("C:/Users/alex-/OneDrive/Desktop/Concrete.csv")
summary(strength)

```
```{r}
any(is.na(strength))
```
There are no missing values in our data set.

In this section, we analyze our data set where we will employ a linear regression model to analyze the impact of various components on the compression strength of concrete. The components and their corresponding measured values are outlined below:"

- Cement: measured in kilograms per cubic meter (kg/m^3).
- Blast Furnace slag: measured in kilograms per cubic meter (kg/m^3).
- Fly Ash: measured in kilograms per cubic meter (kg/m^3).
- Water: measured in kilograms per cubic meter (kg/m^3).
- Superplasticizer: measured in kilograms per cubic meter (kg/m^3).
- Coarse Aggregate: measured in kilograms per cubic meter (kg/m^3).
- Fine Aggregate: measured in kilograms per cubic meter (kg/m^3).
- Age: measured in days.
And the concrete compression strength: 
- Concrete compression strength: measured in megapascals (MPa).


